Arbitrary Code Injection in Adblock Plus

### 2023-05-02 paper/paper.tex
Update figures
Update

\section{Attack Outline}
The attack can be schematized in the fo

\subsection{Victim website}

has an open redirect combined with fetching and loading JS code provokes worse problems.

\subsection{Victim user}

install malicious filter list (may be updated automatically), visit victim website.

\subsection{Attacker}

control the malicious filter list.

\subsection{Potential impact}

@@

\begin{figure}[htp]
     \centering
     \begin{subfigure}[b]{0.5\textwidth}
         \centering
         \includegraphics[width=.9\textwidth]{2-figure}
         \caption{Without the malicious filter, the dynamic JavaScript is loaded on the page.}
         \label{fig:non-vulnerable}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.5\textwidth}
         \centering
         \includegraphics[width=.9\textwidth]{1-figure}
         \caption{With the malicious filter enabled,  AdBlock Plus rewrites the dynamic JavaScript's URL to the open redirect URL, which returns malicious JS code.}
         \label{fig:vulnerable}
     \end{subfigure}
        \caption{Screenshots of a proof of concept website demonstrating the capabilities of the attack.}
        \label{fig:poc}
\end{figure}

@@

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

>>>>

\section{Attack Outline}
The attack can be schematized as follows.

\begin{enumerate}
    \item Victim website: fetches and loads JavaScript (with XMLHttpRequest or similar technique) and has an open redirect vulnerability.
    \item Victim user: has enabled a malicious filter list (from a third party or installed by default), and visits the victim's website.
    \item Attacker: is in control of the malicious filter rule. Archives arbitrary code execution in the client.
\end{enumerate}

See details of the attack in Section \ref{sec:Implementation}.

@@

\begin{figure}[htp]
     \centering
     \begin{subfigure}[b]{0.5\textwidth}
         \centering
         \includegraphics[width=.9\textwidth]{fig-normal}
         \caption{Without the malicious filter, the dynamic JavaScript is loaded on the page.}
         \label{fig:non-vulnerable}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.5\textwidth}
         \centering
         \includegraphics[width=.9\textwidth]{fig-attack}
         \caption{With the malicious filter enabled,  AdBlock Plus rewrites the dynamic JavaScript's URL to the open redirect URL, which returns malicious JS code.}
         \label{fig:vulnerable}
     \end{subfigure}
        \caption{Screenshots of a proof of concept website demonstrating the capabilities of the attack.}
        \label{fig:poc}
\end{figure}

@@
